\begin{refsection}
\section{Simulation Parameters}\label{simulation parameters}
The following table contains spin definitions and recommended simulation parameter ranges for 35 brain metabolites and water. This table is based on literature values and does have some gaps. The recommended ranges represent the minimum and maximum values across physiological and pathological differences. The concentration ranges were scaled to represent [$0.9*min$, $1.1*max$]. To compare a variety of sources and to find the most up-to-date values, please check the GitHub repository. 

The data provided here is an excerpt of the database. So far, data has been compiled from textbooks\cite{DeGraaf2007,DeGraaf2018} and commonly referenced literature sources\cite{Govindaraju2000,Govindaraju2015} for defining the spin systems. The chemical shifts and coupling constants have also been reported from MARRS\cite{Landheer2021} since that is the recommended software for simulating basis sets. MARRS also compiled several sources, including Near et al.'s\cite{Near2013} work describing the GABA spin systems. $T_2$ values were collected from Wyss et al.\cite{Wyss2018} who reported moiety-specific values for selected metabolites and from Gudmundson et al.'s\cite{Gudmundson2023} recent meta-analysis. Concentration ranges were compiled from De Graaf's textbooks\cite{DeGraaf2007,DeGraaf2018} and Gudmundson's meta-analysis\cite{Gudmundson2023}. Macromolecule and lipid nuisance signal characterizations come from Gudmundson et. al\cite{Gudmundson2023} and Hamilton et al.\cite{Hamilton2011}. Finally, Wermter et al.'s\cite{Wermter2017} work describing moiety-level temperature-induced frequency shifts has also been included. The following citations were used to compile the current version of the database. As new information is added, the citation list in the repository will be updated:

% \bibliography{mybibliography}
\printbibliography
% % \bibliography{mybibliography}
% % \putbib

\clearpage
\input{tables/tab:supp:condensed}

\end{refsection}