\section{Results}\label{sec:Results}

\subsection{Simulations}
\input{figures/fig:30ms_samples_clean}
The selection of simulations presented in this section focus on short echo (TE=30ms) 3T PRESS spectra with a spectral width of 2000Hz and randomly sampled parameters. The concentrations were sampled with respect to total creatine (tCr). It is important to note that while pulse sequence implications are integral to the overall simulation process, their detailed exploration is beyond the scope of this work. Therefore, in this study, we report simulations specifically tailored to the PRESS sequence.

The choice of short echo spectra is motivated by their ability to capture a broader range of metabolite peaks compared to long echo spectra. The simulations presented include metabolites sampled from a comprehensive set of common brain metabolites including Asc, Asp, Ch, Cr, GABA, Gln, Glu, GPC, GSH, Lac, mI, NAA, NAAG, PCh, PCr, PE, sI, Tau, and a variety of macromolecular and lipid basis functions. For consistency, the SNR was fixed to 15dB and the chemical shift reference point is set to 4.65ppm.

Fig. \ref{fig:30ms samples curated clean} illustrates clean short echo (TE=30ms) PRESS spectra showcasing various combinations of residual water and baseline contributions. These samples omit spectral artifacts to more clearly highlight the variety that can be achieved by randomly sampling the simulation parameters for the physics model and the baseline and residual water generator. In contrast, Fig. \ref{fig:30ms samples curated dirty} presents a series of simulated PRESS spectra (TE=30ms) with randomly sampled parameters, artifacts, and offsets. The baselines and residual water regions shown sometimes appear to be uncorrelated with the depicted spectra due to additional artifacts that are applied after all of the spectral components are combined. Sophisticated simulations, such as these, are useful for developing and validating artifact removal techniques and spectral fitting protocols.  
\input{figures/fig:30ms_samples_artifacts}

While the pulse sequence implications are acknowledged as an important aspect of MRS simulations, their exploration is beyond the immediate scope of this work. The main objective of this work is take manipulate pre-simulated basis sets until they approximate in vivo spectra. Therefore, the primary machinations of MRS-Sim are the same regardless of the basis functions used. Overall, the presented simulations using the PRESS sequence provide a valuable foundation for understanding the performance and capabilities of the MRS-Sim framework.
